---
title: "My Second Species"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup2, echo=FALSE}
source("/home/jabren26/Brenner-ColbyForecasting/setup.R")
```

## Choosing a Species
For my second species, I am choosing to look at Haddock (scientific name *Melanogrammus aeglefinus*). Haddock, another benthic species, often compete with the Atlantic Wolffish, and Atlantic Wolffish are often the bycatch of haddock fisheries. 

## Setting the Scene
```{r getting_the_data}
obs = read_observations("Melanogrammus aeglefinus")

coast = read_coastline()
db = brickman_database() |>
  filter(scenario == "STATIC", var == "mask")
mask = read_brickman(db)
```

## Lets Get Started
We will start by counting the number of observations per month
```{r counts, include = TRUE}
all_counts = count(st_drop_geometry(obs), month)
```

We will now Create a graph with the selected latitudes and longitudes
```{r observations_graph, include = TRUE}
LON0 = -67
LAT0 = 46
ggplot() +
  geom_sf(data = obs, alpha = 0.2, shape = "circle small", size = 1) +
  geom_sf(data = coast, col = "orange") +
  geom_text(data = all_counts,
            mapping = aes(x = LON0, 
                          y = LAT0, 
                          label = sprintf("n: %i", .data$n)),
            size = 3) + 
  labs(x = "Longitude", y = "Latitude", title = "All observations") +
  facet_wrap(~month)
```
We are now going to thin the observations, and create a count.
```{r thinning_observations, include = TRUE}
thinned_obs = sapply(month.abb,
                     function(mon){ 
                       temp_x = obs |> filter(month == mon)
                       if(nrow(temp_x) ==0) return(NULL)
                       thin_by_cell(temp_x, mask)
                     }, simplify = FALSE) |>
  dplyr::bind_rows() 
thinned_counts = count(st_drop_geometry(thinned_obs), month)
```


We are now going to create a bias map.
```{r bias_map, include = TRUE, warning = FALSE}
bias_map = rasterize_point_density(obs, mask)

ggplot() +
  geom_stars(data = bias_map, aes(fill = count)) +
  scale_fill_viridis_b(na.value = "transparent") +
  geom_sf(data = coast, col = "orange") + 
  labs(x = "Longitude", y = "Latitude", title = "Bias map using all observations")
```

We are now going to figure out how many background points to use, by averaging the total over the 12 months, and then randomly sample for the background using our thinned observations and bias map.
```{r background_count, include = TRUE}
nback_avg = mean(all_counts$n) |>
  round()

obsbkg = sapply(month.abb,
                function(mon){
                  temp_x = thinned_obs |> filter(month == mon)
                  if(nrow(temp_x) == 0) return(NULL)
                  sample_background(temp_x, # <- just this month
                                    mask,
                                    method = "random",  # <-- it needs to know it's a bias map
                                    return_pres = TRUE, # <-- give me the obs back, too
                                    n = nback_avg) |>   # <-- how many points
                    mutate(month = mon, .before = 1)
                }, simplify = FALSE) |>
  bind_rows() |>
  mutate(month = factor(month, levels = month.abb))
```

Like before we are going to drop the geometry and count the total background and presence data for each month, we are then going to open the data in the pipe, create 20 different groups based on month and class, and then randomly sample 1 point.
```{r random_sampling, include = TRUE}
count(st_drop_geometry(obsbkg), month, class)

sampled_data = obsbkg |>
  group_by(month, class) |>
  slice_sample(n=1) 
```

After rereading in the Brickman database, and the covariates, we will add the covariates to our randomly selected points
```{r finishing_data_table, include = TRUE}
db = brickman_database() |> 
  filter(scenario == "PRESENT", interval == "mon")

covars = read_brickman(db, add = "depth")

result = sampled_data |>
  group_by(month) |>
  group_map(
    function(rows, keys){
      if(nrow(rows) == 0) return(NULL)
      brick = slice(covars, "month", rows$month[1])
      values = extract_brickman(brick, rows, form = "wide")
      return(values)
    }, .keep = TRUE
  ) |>
  bind_rows() |>
  select(-.id)

result
```

