---
title: "Wolffish Predictions"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup2, echo=FALSE}
source("/home/jabren26/Brenner-ColbyForecasting/setup.R")
```

```{r load_covar, include=FALSE}
cfg = read_configuration(scientificname = "Anarhichas lupus",
                         version = "v1", 
                         path = data_path("models"))
db = brickman_database()
db = brickman_database()
present_conditions = read_brickman(db |> filter(scenario == "PRESENT", 
                                                interval == "mon"),
                       add = c("depth", "month")) |>
  select(all_of(cfg$keep_vars))

model_fits = read_model_fit(filename = "Anarhichas_lupus-v1-model_fits")
```

# Creating the Nowcast

Here is the nowcast projection:
```{r nowcast, echo = FALSE}
nowcast = predict_stars(model_fits, present_conditions)
plot_prediction(nowcast['default_rf'])
```

Here is the nowcast presence and absence projections:
```{r plot_class_labels, warning = FALSE, echo = FALSE}
pa_nowcast = threshold_prediction(nowcast)
plot_prediction(pa_nowcast['default_rf'])
```

# Creating the Forecasts for 2055

Here is the forecast for the year 2055 under the RCP45 conditions (greenhouse emissions taper after the year 2040):
```{r load_2055_RCP45, warning = FALSE, echo = FALSE}
covars_rcp45_2055 = read_brickman(db |> filter(scenario == "RCP45", 
                                               year == 2055, 
                                               interval == "mon"),
                                  add = c("depth", "month")) |>
  select(all_of(cfg$keep_vars))

forecast_rcp45_2055 = predict_stars(model_fits, covars_rcp45_2055)

plot_prediction(forecast_rcp45_2055['default_rf'])
```

Here is the forecast for the year 2055 under the RCP85 conditions (greenhouse emissions continue as is):
```{r load_2055_RCP85, warning = FALSE, echo = FALSE}
covars_rcp85_2055 = read_brickman(db |> filter(scenario == "RCP85", 
                                               year == 2055, 
                                               interval == "mon"),
                                  add = c("depth", "month")) |>
  select(all_of(cfg$keep_vars))

forecast_rcp85_2055 = predict_stars(model_fits, covars_rcp85_2055)

plot_prediction(forecast_rcp85_2055['default_rf'])
```

# Creating the Forecasts for 2075

Here is the forecast for the year 2075 under the RCP45 conditions (greenhouse emissions taper after the year 2040):
```{r load_2075_RCP45, warning = FALSE, echo = FALSE}
covars_rcp45_2075 = read_brickman(db |> filter(scenario == "RCP45", 
                                               year == 2075, 
                                               interval == "mon"),
                                  add = c("depth", "month")) |>
  select(all_of(cfg$keep_vars))

forecast_rcp45_2075 = predict_stars(model_fits, covars_rcp45_2075)

plot_prediction(forecast_rcp45_2075['default_rf'])
```

Here is the forecast for the year 2075 under the RCP85 conditions (greenhouse emissions continue as is):
```{r load_2075_RCP85, warning = FALSE, echo = FALSE}
covars_rcp85_2075 = read_brickman(db |> filter(scenario == "RCP85", 
                                               year == 2075, 
                                               interval == "mon"),
                                  add = c("depth", "month")) |>
  select(all_of(cfg$keep_vars))

forecast_rcp85_2075 = predict_stars(model_fits, covars_rcp85_2075)

plot_prediction(forecast_rcp85_2075['default_rf'])
```


```{r save_pred, echo=FALSE}
# make sure the output directory exists
path = make_path("predictions")

write_prediction(nowcast,
                 scientificname = cfg$scientificname,
                 version = cfg$version,
                 year = "CURRENT",
                 scenario = "CURRENT")
write_prediction(forecast_rcp45_2055,
                 scientificname = cfg$scientificname,
                 version = cfg$version,
                 year = "2055",
                 scenario = "RCP45")
write_prediction(forecast_rcp85_2055,
                 scientificname = cfg$scientificname,
                 version = cfg$version,
                 year = "2055",
                 scenario = "RCP85")
write_prediction(forecast_rcp45_2075,
                 scientificname = cfg$scientificname,
                 version = cfg$version,
                 year = "2075",
                 scenario = "RCP45")
write_prediction(forecast_rcp85_2075,
                 scientificname = cfg$scientificname,
                 version = cfg$version,
                 year = "2075",
                 scenario = "RCP85")
```