---
title: "Wolffish Models"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup2, echo=FALSE}
source("/home/jabren26/Brenner-ColbyForecasting/setup.R")
```

```{r load_data, include = FALSE}
cfg = read_configuration(scientificname = "Anarhichas lupus", version = "v1")
model_input = read_model_input(scientificname = "Anarhichas lupus", 
                               version = "v1",
                               log_me = c("depth", "Xbtm")) |>
  dplyr::mutate(month = month_as_number(.data$month)) |>
  select(all_of(c("class", cfg$keep)))
```

#Examining the Split
```{r initial_split, include = FALSE}
model_input_split = spatial_initial_split(model_input, 
                        prop = 1 / 5,     
                        strategy = spatial_block_cv) 
```

After having split the data into training and testing data, here is a spacial image of the training and testing data.
```{r initial_split_plot, echo = FALSE}
autoplot(model_input_split)
```

We then split the training data into different mini-datasets for training shown here:
```{r cv_training, echo = FALSE}
tr_data = training(model_input_split)
cv_tr_data <- spatial_block_cv(tr_data,
  v = 5,     
  cellsize = grid_cellsize(model_input),
  offset = grid_offset(model_input) + 0.00001
)
autoplot(cv_tr_data)
```

#Planning the Analysis 

Now that we have the data all split up, we are going to create a recipe that defines what the different variables signify (predictor, coordinates, and outcomes).
```{r build_analysis, echo = FALSE}
one_row_of_training_data = dplyr::slice(tr_data,1)
rec = recipe(one_row_of_training_data, formula = class ~ .)
summary(rec)
```

With our variables all defined, we can begin preparing the analysis by defining the workflows for the different models:
- Logistic Regression
- Random Forest
- Boosted Tree
- Max Entropy

```{r make_workflow, include = FALSE}
wflow = workflow_set(
  
  preproc = list(default = rec), 
  
  models = list(                 
    
      
      glm = logistic_reg(
          mode = "classification") |>
        set_engine("glm"),
      
      
      rf = rand_forest(
          mtry = tune(),
          trees = tune(),
          mode = "classification") |>
        set_engine("ranger", 
                   importance = "impurity"),
      
      
      btree = boost_tree(
          mtry = tune(), 
          trees = tune(), 
          tree_depth = tune(), 
          learn_rate = tune(), 
          loss_reduction = tune(), 
          stop_iter = tune(),
          mode = "classification") |>
        set_engine("xgboost"),
      
      maxent = maxent(
          feature_classes = tune(),
          regularization_multiplier = tune(),
          mode = "classification") |>
        set_engine("maxnet")
  )
)
```

And also our different success metrics:
- Accuracy
- Boyce Continuous
- Area Under the Curve
- TSS

```{r metrics, include = FALSE}
metrics = sdm_metric_set(yardstick::accuracy)
```

These metrics will help the models determine the accuracy and attempt to maximize their correctness, allowing them to adjust their hyperparameters. 

```{r fit, warning = FALSE, include = FALSE}
wflow <- wflow |>
  workflow_map("tune_grid",
    resamples = cv_tr_data, 
    grid = 3,
    metrics = metrics, 
    verbose = TRUE)
```

#Picking the Best

The results of the different models and there successes across the different metrics are shown here: 
```{r plot_wflow, echo = FALSE}
autoplot(wflow)
```

We then select the best configuration of hyperparameters for each model so we can better analyze the models success. From this we can pull summary statistics:
```{r select_best, echo = FALSE}
model_fits = workflowset_selectomatic(wflow, model_input_split,
                                  filename = "Anarhichas_lupus-v1-model_fits",
                                  path = data_path("models"))

model_fit_metrics(model_fits)
```

Confusion Matrices:
```{r confusion_matrix, echo = FALSE}
model_fit_confmat(model_fits)
```

And AUC Plots:
```{r auc_plot, echo = FALSE}
model_fit_roc_auc(model_fits)
```
```{r model_fit_vip}
model_fit_varimp_plot(model_fits)
```


#Examining the Random Forest
Using the same testing and training data from earlier:
```{r random_forest, echo = FALSE}
rf = model_fits |>
  filter(wflow_id == "default_rf")

autoplot(rf$splits[[1]])
```

The random forest used the metrics we set to tune for the best hyperparameters, which had these metrics associated with them:
```{r success_metrics, echo = FALSE}
rf$.metrics[[1]]
```

And then created these predictions:
```{r rf_preds, echo = FALSE}
rf$.predictions[[1]]
```

Here is the overall workflow for the random forest model:
```{r workflow_2, echo = FALSE}
rf$.workflow[[1]]
```

#Partial Dependence Plot 

We then created a partial dependence plot for the best performing model... the random forest model
```{r pd_plot, echo = FALSE}
model_fit_pdp(model_fits, wid = "default_rf", title = "Random Forest")
```





